\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex
Fixed references, added beginning of expected outcomes

\section{Expected Outcomes}
Words

@@

\bibliographystyle{ieee}
\bibliography{references}

>>>>

\section{Expected Outcomes}
Not every penetration test finds a massive zero day vulnerability.  However, that doesn't mean a test isn't completely useless.  Tests may not often discover massive issues, but smaller issues are often prevalent.  Issues such as weaker cryptography, bad hardware intrusion detection, and magnetic locking overrides are common in locking hardware.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
